---
title: "Project 3 - Example Main Script"
author: "Yuting Ma, Tian Zheng"
date: "February 24, 2016"
output:
  pdf_document: default
  html_document: default
---
In your final repo, there should be an R markdown file that organizes **all computational steps** for evaluating your proposed image classification framework. 

This file is currently a template for running evaluation experiments of image analysis (or any predictive modeling). You should update it according to your codes but following precisely the same structure. 

```{r}
if(!require("xgboost")){
  install.packages("xgboost")
}

if(!require("ggplot2")){
  install.packages("ggplot2")
}

if(!require("reshape2")){
  install.packages("reshape2")
}

library(xgboost)
library(ggplot2)
library(reshape2)

source("../lib/xgboost_cv.R")
```

### Step 0: specify directories.

Provide directory for extracted features.
```{r}
feat.dir <- "../output/features/"
```

### Step 1: set up controls for evaluation experiments.

In this chunk, ,we have a set of controls for the evaluation experiments. 

+ (T/F) cross-validation on the training set
+ (number) K, the number of CV folds
+ (T/F) process features for training set
+ (T/F) run evaluation on an independent test set
+ (T/F) process features for test set

```{r exp_setup}
run.cv=TRUE # run cross-validation on the training set
K <- 5  # number of CV folds
run.test=TRUE # run evaluation on an independent test set
```


### Step 2: import training features and labels.

```{r train_label}
sift2 <- read.csv(paste0(feat.dir, "SIFT_train1.csv"))
load(paste0(feat.dir, "hog_train1.RData"))
lbp2 <- read.csv(paste0(feat.dir, "lbp_train1.csv"))
train2 <- cbind(sift2, hog2, lbp2)
train2 <- data.matrix(train2)

lab_tr <- read.csv(paste0(feat.dir, "label_train1.csv"))
lab_tr <- data.matrix(lab_tr)
```


### Step 3: Train a classification model with training images

#### Model selection with cross-validation
* Do model selection by choosing among different values of training model parameters, that is, the interaction depth for GBM in this example. 
```{r runcv, message=FALSE, warning=FALSE}

if(run.cv){
  shl_tr <- xgboost_cv(train = train2, lab = lab_tr, nrou = 300, 
                      list_max.depth = c(3, 5, 10, 20), 
                      list_eta = c(0.03, 0.3, 0.5, 0.8),
                      name = "SIFT + HOG + lbp", fold = K)
  err.cv1 <- shl_tr[[1]]
  save(err.cv1, file = "../XGBOOST_results/err_shl.csv")
  
  print(shl_tr[[2]])
  
  shl_tr2 <- xgboost_cv(train = train2, lab = lab_tr, nrou = 200, 
                      list_max.depth = c(2, 3, 4), 
                      list_eta = c(0.4, 0.5),
                      name = "SIFT + HOG + lbp 2", fold = K)
  err.cv2 <- shl_tr2[[1]]
  save(err.cv2, file = "../XGBOOST_results/err_shl2.csv")
}
```

Visualize cross-validation results. 

```{r cv_vis}
if(run.cv){
  print(shl_tr[[2]])
  
}
```


* Train the model with the entire training set using the selected model (model parameter) via cross-validation.
```{r final_train}
tm_train=NA
param <- list("objective" = "multi:softmax",
                    "num_class" = 4,
                    "eta" = 0.5, "max.depth" = 4)
tm_train <- system.time(bst <- xgboost(data = train2, label = lab_tr, params = param, nrounds = 80, verbose = 0))
save(bst, file="../output/XGBOOST_results/bst.RData")
```

### Step 5: Make prediction 
Feed the final training model with the completely holdout testing data. 
```{r test}
tm_test=NA
if(run.test){
  sift1 <- read.csv(paste0(feat.dir, "SIFT_test1.csv"))
  load(paste0(feat.dir, "hog_test1.RData"))
  lbp1 <- read.csv(paste0(feat.dir, "lbp_test1.csv"))
  test <- cbind(sift1, hog1, lbp1)
  test <- data.matrix(test)
  
  tm_test <- system.time(pred <- predict(bst, test))
  save(pred, file="../output/XGBOOST_results/pred_test.RData")
  
  lab_te <- read.csv(paste0(feat.dir, "label_test1.csv"))
  mean(pred != lab_te)
}
```

### Summarize Running Time
Prediction performance matters, so does the running times for constructing features and for training the model, especially when the computation resource is limited. 
```{r running_time}
cat("Time for training model=", tm_train[3], "s \n")
cat("Time for making prediction=", tm_test[3], "s \n")
```
